resistanceModelNotesAndy

### 2015-03-11 resistanceModelNotesAndy.Rmd
progress notes

**11/3/15** 9.30

@@

@@

>>>>

**11/3/15** 9.30-12.30 3hrs 2.15-6.45 7.5hrs

@@

Plan
1. move Beths functions out into a single file for each in an R folder
1. edit Beths commments into roxygen format
1. only later think about changing functions and documentation to follow best practice

Changed plan slightly by appending plot onto start of plot functions.

To source files in the R folder
`lapply(dir("R"),function(x) source(paste0("R//",x)))`

@@

### suggestion from Beth
looking at it now I realise this is not ideal
a solution may be to provide a .csv file with the Curtis scenarios set up
and then the need to set the calibration number and params.csv in the R script can be removed altogether
so it is all set up in the .csv file - I think similar can be done with produce.plots
so the only bit of R code the user will need to change is the setwd() and the read.csv()
